### 2014-07-09 brains-protocol.tex
Some figures renamed

\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/feature_correlations-filter1.png}
    \caption{Spearman correlations in the initial set of features}
    \label{fig:feature-corrs-initial}
\end{figure}

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.6975\linewidth]{images/computed-figures/feature_correlations-filter2.png}
    \caption{Spearman correlations in the filtered set of features}
    \label{fig:feature-corrs-filtered}
\end{figure}

@@

\begin{figure*}[th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution_recursive_min20_no-exclusion.png}
    \caption{\textbf{Feature distribution evolution:} evolution of the distribution of feature values in substitution chains over successive 2-day time bags (bags 0 to 18, i.e. days 0 to 37).
    The legends indicate the number of words left in each time bag; these decrease exponentially since only a fraction of the quotes undergo substitution at each step.
    After a period of time, each feature becomes concentrated in a specific range of its own.}
    \label{fig:timebags-evolution}
\end{figure*}

>>>>

\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/correlations-filter1.png}
    \caption{Spearman correlations in the initial set of features}
    \label{fig:feature-corrs-initial}
\end{figure}

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.6975\linewidth]{images/computed-figures/correlations-filter2.png}
    \caption{Spearman correlations in the filtered set of features}
    \label{fig:feature-corrs-filtered}
\end{figure}

@@
